 

### 2023-05-16 appendix_2.1.Rmd
Revisions to tables, revised submission to ProQuest

```{r  table_s_2_2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

mh_english_disease %>% unique() %>%
  arrange(disease) %>%
  relocate(disease, .before=disease_english) %>%
    mutate(disease = gsub(" and ", " & ", disease),
           disease =  StrTrunc(disease, maxlen = 40, ellipsis = "...", wbound = TRUE),
           disease_english = gsub(" and ", " & ", disease_english),
   disease_english = case_when(
       str_detect(disease_english, "Bouffées délirantes aiguës") ~
                   "Short-lived psychosis",
   TRUE ~ disease_english),
      disease_english = gsub("of diseases classified elsewhere", "(d.c.e.)", disease_english),
      disease_english = gsub("in diseases classified elsewhere", "(d.c.e.)", disease_english),
   disease_english = gsub(" nervous system", " N.S.", disease_english)) %>%
  rename(English = disease_english, French = disease) %>%
  gt() %>%
  tab_footnote(
    footnote = "d.c.e.: in or among diseases classified elsewhere. N.S.: nervous system",
    locations = cells_column_labels(
      columns = English
    )
  ) %>%
  tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold", size = 9))) %>%
    tab_header(
    title ="Table S2.2: Mental health disorders reported in GESIS, in French and English")

@@

```{r  reporting_tables1a, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(csb_data, "Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities")

@@

```{r  reporting_tables1b, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(chd_data, "Table S2.4: Yearly cumulative visits for mental and neurological disorders reported at district hospitals")

@@

```{r  reporting_tables2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(chu_data, "Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals")

>>>>

```{r table_s_2_2, echo = FALSE, include = TRUE, out.width = '97%'}

knitr::include_graphics("table_s_2_2.png")

# 
# mh_english_disease %>% unique() %>%
#   arrange(disease) %>%
#   relocate(disease, .before=disease_english) %>%
#     mutate(disease = gsub(" and ", " & ", disease),
#            disease =  StrTrunc(disease, maxlen = 40, ellipsis = "...", wbound = TRUE),
#            disease_english = gsub(" and ", " & ", disease_english),
#    disease_english = case_when(
#        str_detect(disease_english, "Bouffées délirantes aiguës") ~
#                    "Short-lived psychosis",
#    TRUE ~ disease_english),
#       disease_english = gsub("of diseases classified elsewhere", "(d.c.e.)", disease_english),
#       disease_english = gsub("in diseases classified elsewhere", "(d.c.e.)", disease_english),
#    disease_english = gsub(" nervous system", " N.S.", disease_english)) %>%
#   rename(English = disease_english, French = disease) %>%
#   gt() %>%
#   tab_footnote(
#     footnote = "d.c.e.: in or among diseases classified elsewhere. N.S.: nervous system",
#     locations = cells_column_labels(
#       columns = English
#     )
#   ) %>%
#   tab_style(locations = cells_column_labels(),
#             style     = list(cell_text(weight = "bold", size = 9))) %>%
#     tab_header(
#     title ="Table S2.2: Mental health disorders reported in GESIS, in French and English")  %>%
#    gtsave("table_s_2_2.docx")

@@

```{r  reporting_tables1a, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}

knitr::include_graphics("table_s_2_3.png")

# 
# reporting_table(csb_data, "Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities")  %>%
#    gtsave("table_s_2_3.docx")

@@

```{r  reporting_tables1b, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}

knitr::include_graphics("table_s_2_4.png")

# reporting_table(chd_data, "Table S2.4: Yearly cumulative visits for mental and neurological disorders reported at district hospitals") %>%
#    gtsave("table_s_2_4.docx")

@@

```{r  reporting_tables2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}

knitr::include_graphics("table_s_2_5a.png")
knitr::include_graphics("table_s_2_5b.png")

# reporting_table(chu_data, "Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals") %>%
#    gtsave("table_s_2_5.docx")
